\textbf{Computational Fuzzy Extractors}

### 2013-05-17 CompFuzzExt.tex
fixing conductor badness

\newcommand{\ve}{\vect{e}}
\newcommand{\vm}{\vect{m}}
\newcommand{\vy}{\vect{y}}
\newcommand{\vE}{\vect{E}}
\newcommand{\vS}{\vect{S}}
\newcommand{\vA}{\vect{A}}
\newcommand{\vc}{\vect{c}}
\newcommand{\vW}{\vect{W}}
\newcommand{\vR}{\vect{R}}
\newcommand{\vU}{\vect{U}}
\newcommand{\vT}{\vect{T}}
\newcommand{\vX}{\vect{X}}
\newcommand{\vB}{\vect{B}}
\newcommand{\vz}{\vect{z}}
\newcommand{\vd}{\vect{d}}
\newcommand{\vs}{\vect{s}}
\newcommand{\vx}{\vect{x}}
\newcommand{\va}{\vect{a}}
\newcommand{\vb}{\vect{b}}
\newcommand{\vgamma}{\mathbf{\Gamma}}
\newcommand{\vt}{\vect{t}}
\newcommand{\vu}{\vect{u}}
\newcommand{\vF}{\vect{F}}
\newcommand{\recout}{x}
\newcommand{\ignore}[1]{}

@@

\item\textbf{Positive Result:} We show that the negative result can be overcome by
analyzing computational fuzzy extractors directly.  Namely, we show
how to build a computational fuzzy extractor whose output key length
equals the entropy of the source (this is impossible in the
information-theoretic setting). Our construction is based on the
hardness of the Learning with Errors (LWE) problem, and is secure when
the noisy source is uniform or symbol-fixing (that is, each dimension
is either uniform or fixed). As part of the security proof, we show a result of independent interest, namely
that the decision version of LWE is secure even when a small number of
dimensions has no error.
\end{itemize}
\end{abstract}

\newcommand{\M}{\mathcal{M}}
\section{Introduction}\label{sec:introduction}

@@

%~\ref{thm:lossless secure conductor log})).  We demonstrate how to build such lossless conductors based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult. 

@@

We review definitions of Shannon codes~\cite{shannon1949mathematical}:
\begin{definition}
\label{def:shannon-code}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]\le \epsilon$. To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
\end{definition}
This is a slightly stronger formulation than usual, in that for every size  $t'<t$ we require the code to correct $t'$ random errors \footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compared to the volume of the ball of size $t$.  For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.  However, we work with an arbitrary recover functionality that is not necessarily monotone.}.

@@

\subsection{Bounds on Secure Sketches using Unpredictability Entropy}
\label{sec:imp unp sketch}
In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.  However, HILL entropy is a strong notion.  In this section, we therefore ask whether it is useful to consider a sketch that satisfies a minimal requirement: the value of the input is computationally hard to guess given the sketch.  We begin by recalling the definition of conditional unpredictability entropy, which captures the notion of ``hard to guess'' (we relax it similar to the way conditional HILL entropy was relaxed in the previous section).

@@

\begin{theorem}
\label{thm:lossless secure conductor log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d)$.  Let $W$ be uniform over $\zo^{(c+2d)nb/d}$.  If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.  That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\vA, \vA X+W) = n/2\log q = H_\infty(W)$
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
with 
$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch runs in time $O(n^3\log n)$, and recover takes expected time $O(n^{4d+3} \log n)$ with error probability $\delta = e^{-\Omega(n)}$ over the choice of $\vA$.
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}.
\end{proof}

For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
\thref{thm:lossless secure conductor log} shows that a computational fuzzy conductor can be built without incurring any entropy loss.  This is essentially due to $\vA X+W$ looking like a uniformly random point and providing no information about either $X$ or $W$.  
%A natural question to ask is whether security degrades gracefully when $W$ is not the uniform distribution.  We begin to provide an answer in \secref{sec:LWE block fixing sources}.

@@

@@

\ignore{
\subsection{\consref{cons:informal construction} with slightly deficient sources}
\label{sec:DP general error LWE}
In this section, we discuss how to generalize \consref{cons:informal construction} to an arbitrary high min-entropy distribution.  We will show security using a result of Micciancio and Peikert~\cite{micciancio2013hardness}.  This result allows us to argue security for an arbitrary distribution that is nearly high entropy.  This result should be seen as a complement to the proceeding sections.  It allows for a more general error distribution, but with worse parameters than \thref{thm:lossless secure conductor log}.  Also \thref{thm:lossless block sketch log} allows for more deficient sources but of a more restricted form~(symbol fixing sources).
\begin{theorem}
Let $n$ be a security parameter and let $m=cn, \ell = m-n/2$.  Let $C$ be a constant and define the parameter $\rho \geq (Cm)^{\frac{m-n/2}{n/2}} = (Cm)^{2c-1}$ and let $q$ be a prime where $\poly(n) = q\geq (4\rho)^{\frac{c}{c-1}}$.  Consider a distribution $\chi$ over the space $\{-\rho, ..., \rho \}^m$.  If $\Hoo(\chi)\geq m\log \rho$ and SIVP is hard to approximate in the worst case for quantum algorithms within an approximation factor of $\gamma=\tilde{O}(\sqrt{n} q)$~(on lattices of $n/2$ dimensions), then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
\end{theorem}
\textbf{Note:}  The above theorem is a generalized version of~\cite[Theorem 4.6]{micciancio2013hardness}.  In particular, we note the requirement of sampling from the uniform distribution over some set $\chi \subset \{-\rho,..., \rho\}^m$ is not necessary.  The only requirement in the proof is that $|\chi|\geq m\log \rho$.  Requiring that $\Hoo(\chi) = m\log \rho$ implies that the support of $\chi$ contains at least $2^{m\log \rho}$ elements.  This theorem allows all distributions over a space of size $(2\rho)^m$ that have entropy at least $m\log \rho$.  This means we support all distributions whose entropy gap is no more than $m$ bits.

@@

%\section{Computational Fuzzy Extractors}
%In this section, we show that any computational secure sketch implies a computationally fuzzy extractor using the same paradigm as \lemref{lem:fuzzy ext construction}.  We begin with a formal definition of a computational fuzzy extractor:
%\label{sec:comp fuzzy extractors}
%
%
%Average-case extractors produce pseudorandom bits if the input distribution has high HILL entropy:
%\begin{lemma}
%Let $\ext: \chi \times \zo^d \rightarrow \zo^\ell \times \zo^d$ be a $(k, \epsilon_{ext})$-extractor computable by a circuit of size $s_{ext}$.  Let $X$ be a distribution over $\chi$ with $H^{\hill}_{\epsilon, s_{sec}}(X| Z)\geq k$.  Let, $s' = s_{sec}-s_{ext}$, then 
%$H^{\hill}_{\epsilon+\epsilon_{ext}, s_{sec}}(\ext (X, U_d) | Z, U_d)\geq \ell$.
%\end{lemma}
%%  the same paradigm from 
%%Recall, we defined computational secure sketches using unpredictability entropy~(\defref{def:comp secure sketch}).  It is not known if unpredictability entropy can be extracted from, so we cannot use the construction of \lemref{lem:fuzzy ext construction}.  However, unpredictability entropy implies Yao entropy~(\defref{def:yao entropy}) and this can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}).  
%%\begin{definition}
%%An $(\ell, \epsilon)$-reconstruction for a function $\rext:\{0,1\}^n\times \{0,1\}^d\rightarrow \{0,1\}^m\times\{0,1\}^d$~(where the last $d$ outputs are equal to the last $d$ input bits) is a pair of machines $C$ and $D$, where $C:\{0,1\}^n\rightarrow \{0,1\}^\ell$ is a randomized Turing machine and $D^{(\cdot)}:\{0,1\}^\ell\rightarrow \{0,1\}^n$ is a randomized oracle Turing machine which runs in time polynomial in $n$.  Furthermore, for every $x$ and $T$, if $|\Pr[T(\rext(x, U_d)) =1] -\Pr[T(U_m\times U_d)=1]|>\epsilon$, then $\Pr[D^T(C^T(x))=x]>1/2$~(the probability is over the random choices of $C$ and $D$).
%%\end{definition}
%%\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
%%\label{lem:unp extraction} 
%%Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.  Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
%%\end{lemma}
%We are now ready to provide a computational analogue of \lemref{lem:fuzzy ext construction}:
%\begin{lemma}
%Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon, s_{sec})$ hard with error $\delta$ and denote the range $\rec$ by $\chi$.  Let $\ext:\chi \times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an $(\tilde{m}, \epsilon_{ext})$ extractor.  Then the following $(\gen , \rep)$ is an $(\mathcal{M}, m, \ell, t)$-computational fuzzy extractor that is $(\epsilon + \epsilon_{ext}, s_{sec}- s_{ext})$-hard with error $\delta$.
%\end{lemma}
%%reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, s_{sec}/(|C|+|D|), s_{rec}, 5\epsilon)$-computational fuzzy extractor:
%%\begin{itemize}
%%\item $\gen(w;r, x)$: set $P= (\sketch(w; r), x), R = \rext(w, x)$, and output $(R,P)$.
%%\item $\rep(w', (s, x)):$ recover $w = \rec(w', s)$ and output $R = \rext(w;x)$.
%%\end{itemize}
%%\end{lemma}
%%\begin{proof}
%%Consequence of \defref{def:comp secure sketch} and \lemref{lem:unp extraction}.
%%\end{proof}
%%
%%For completeness, we describe a computational fuzzy extractor based on Construction~\ref{cons:LWESecureSketch} in \secref{sec:fuzzy extractor phrasing}.

@@

\section{Parameter Settings for \consref{cons:informal construction}}
\label{sec:parameter settings}
In this section, we explain the different parameters that go into our construction.  In \thref{thm:lossless secure conductor log} we give lossless conductors from a security parameter $n$ and an error $t$.  In this section, we discuss constraints imposed by 1) efficient decoding 2) maintaining security of the LWE instance and 3) ensuring no entropy loss of the construction.  We begin by reviewing the parameters that make up our construction:

@@

Assuming $n-k = n(1-1/g) > n_0$ and letting $t= c\log n$ we get the following setting:
\begin{align*}
m &= \frac{(c+2d)n}{d}\\
q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m}{\log n}} = \poly(n)\\
\rho q &= 2n^{1/2+3\gamma}m = \frac{2(c+2d)n^{3/2+3\gamma}}{d}
\end{align*}
Furthermore, we get decoding in time $O(n^{4d}(n^3\log n))$.  We can output a $k$ fraction of $X$ and the bits will be pseudorandom~(conditioned on $\vA, \vA X+W$).  The parameter $g$ allows is a tradeoff between the number of dimensions needed for security and the size of the field $q$.  In \thref{thm:lossless secure conductor log}, we set $g=2$ and output the first half of $X$.  This analysis proceeds similarly when we desire a linear stretch instead of $m\log \rho q = k\log q$.  %Essentially, this corresponds to multiplying $g$ by the inverse of the desired stretch factor.

>>>>

\newcommand{\ve}{\vect{e}}
\newcommand{\vm}{\vect{m}}
\newcommand{\vy}{\vect{y}}
\newcommand{\vE}{\vect{E}}
\newcommand{\vS}{\vect{S}}
\newcommand{\vA}{\vect{A}}
\newcommand{\vc}{\vect{c}}
\newcommand{\vW}{\vect{W}}
\newcommand{\vR}{\vect{R}}
\newcommand{\vU}{\vect{U}}
\newcommand{\vT}{\vect{T}}
\newcommand{\vX}{\vect{X}}
\newcommand{\vB}{\vect{B}}
\newcommand{\vz}{\vect{z}}
\newcommand{\vd}{\vect{d}}
\newcommand{\vs}{\vect{s}}
\newcommand{\vx}{\vect{x}}
\newcommand{\va}{\vect{a}}
\newcommand{\vb}{\vect{b}}
\newcommand{\vgamma}{\mathbf{\Gamma}}
\newcommand{\vt}{\vect{t}}
\newcommand{\vu}{\vect{u}}
\newcommand{\vF}{\vect{F}}
\newcommand{\recout}{x}
\newcommand{\ignore}[1]{}
\newcommand{\M}{\mathcal{M}}

@@

\item\textbf{Positive Result:} We show that the negative result can be overcome by
analyzing computational fuzzy extractors directly.  Namely, we show
how to build a computational fuzzy extractor whose output key length
equals the entropy of the source (this is impossible in the
information-theoretic setting). Our construction is based on the
hardness of the Learning with Errors (LWE) problem, and is secure when
the noisy source is uniform or symbol-fixing (that is, each dimension
is either uniform or fixed). As part of the security proof, we show a result of independent interest, namely
that the decision version of LWE is secure even when a small number of
dimensions has no error.
\end{itemize}
\textbf{Keywords} Fuzzy extractors, secure sketches, key derivation, Learning with Errors, noise tolerance, error-correcting codes, computational entropy, randomness extractors.
\end{abstract}

\section{Introduction}\label{sec:introduction}

@@

%~\ref{thm:lossless secure extractor log})).  We demonstrate how to build such lossless conductors based on the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey},  which says that decoding a random linear code is computationally difficult. 

@@

We review definitions of Shannon codes~\cite{shannon1949mathematical}:
\begin{definition}
\label{def:shannon-code}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$ and for all $c\in \mathcal{C}$, $\Pr[\rec(\neigh(c, t')) \neq c]\le \epsilon$. To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
\end{definition}
This is a slightly stronger formulation than usual, in that for every size  $t'<t$ we require the code to correct $t'$ random errors\footnote{In the standard formulation, the code must correct a random error of size up to $t$, which may not imply that it can correct a random error of a much smaller size $t'$, because the volume of the ball of size $t'$ may be negligible compared to the volume of the ball of size $t$.  For codes that are monotone~(if decoding succeeds on a set of errors, it succeeds on all subsets), these formulations are equivalent.  However, we work with an arbitrary recover functionality that is not necessarily monotone.}.

@@

\subsection{Bounds on Secure Sketches using Unpredictability Entropy}
\label{sec:imp unp sketch}
In the previous section, we showed that any sketch that retained HILL entropy could be transformed into an information theoretic sketch.  However, HILL entropy is a strong notion.  In this section, we therefore ask whether it is useful to consider a sketch that satisfies a minimal requirement: the value of the input is computationally hard to guess given the sketch.  We begin by recalling the definition of conditional unpredictability entropy, which captures the notion of ``hard to guess'' (our relaxation is analogous to relaxed HILL entropy described in the previous section).

@@

\begin{theorem}
\label{thm:lossless secure extractor log}
Let $n$ be a security parameter and let $t = c\log n$ for some constant $c$.  Let $d\in \mathbb{Z}^+$ be a constant and consider the Hamming metric with block length $b = \log (2n^3 (c+2d)/d)$.  Let $W$ be uniform over $\zo^{(c+2d)nb/d}$.  If GAPSVP and SIVP are hard to approximate within polynomial factors~(on lattices of dimension $n/4$) using quantum algorithms, then there is a setting of $q = \poly(n)$ such that \consref{cons:informal construction} is a lossless fuzzy extractor.  That is, $H^{\hill}_{\epsilon, s_{sec}}(X_{1,..., n/2}|\vA, \vA X+W) = n/2\log q = H_\infty(W)$
% for following parameters:
%\[
%(\zo^{(c+d)/dn\log b}, |W|, \epsilon, s_{sec}, s_{sketch}, s_{rec}, t)
%\] 
with 
$\epsilon = \ngl(n), s_{sec} = \poly(n)$,  sketch runs in time $O(n^3\log n)$, and recover takes expected time $O(n^{4d+3} \log n)$ with error probability $\delta = e^{-\Omega(n)}$ over the choice of $\vA$.
\end{theorem}
\begin{proof}
Security follows by combining Lemmas~\ref{lem:uniform LWE decision} and~\ref{lem:many hardcore bits}, efficiency follows by \lemref{lem:i t poly time}.
\end{proof}

For a more detailed explanation of the various parameters and constraints see \secref{sec:parameter settings}.  In particular, we describe how to set $q = \poly(n)$.  
\thref{thm:lossless secure extractor log} shows that a computational fuzzy extractor can be built without incurring any entropy loss.  This is essentially due to $\vA X+W$ looking like a uniformly random point and providing no information about either $X$ or $W$.  
%A natural question to ask is whether security degrades gracefully when $W$ is not the uniform distribution.  We begin to provide an answer in \secref{sec:LWE block fixing sources}.

@@

%However, the construction of a computational fuzzy extractor by 
%The advantage of \consref{cons:informal construction} is that losses due to error correction $O(\log |B_t(\cdot)|)$ and randomness extraction $O(\log 1/\epsilon)$ are not necessary.  In the case where $W$ is small, these losses may leave too few bits for a secure pseudorandom generator.  The work of~\cite{dachman2012computational} shows that these losses in the extract-then-expand construction are in some sense necessary~(the samplable RT conjecture in~\cite{dachman2012computational} has been resolved positively by~\cite{dodis2013key}).

@@

\ignore{
\subsection{\consref{cons:informal construction} with slightly deficient sources}
\label{sec:DP general error LWE}
In this section, we discuss how to generalize \consref{cons:informal construction} to an arbitrary high min-entropy distribution.  We will show security using a result of Micciancio and Peikert~\cite{micciancio2013hardness}.  This result allows us to argue security for an arbitrary distribution that is nearly high entropy.  This result should be seen as a complement to the proceeding sections.  It allows for a more general error distribution, but with worse parameters than \thref{thm:lossless secure extractor log}.  Also \thref{thm:lossless block sketch log} allows for more deficient sources but of a more restricted form~(symbol fixing sources).
\begin{theorem}
Let $n$ be a security parameter and let $m=cn, \ell = m-n/2$.  Let $C$ be a constant and define the parameter $\rho \geq (Cm)^{\frac{m-n/2}{n/2}} = (Cm)^{2c-1}$ and let $q$ be a prime where $\poly(n) = q\geq (4\rho)^{\frac{c}{c-1}}$.  Consider a distribution $\chi$ over the space $\{-\rho, ..., \rho \}^m$.  If $\Hoo(\chi)\geq m\log \rho$ and SIVP is hard to approximate in the worst case for quantum algorithms within an approximation factor of $\gamma=\tilde{O}(\sqrt{n} q)$~(on lattices of $n/2$ dimensions), then $\distLWE_{n, m, q, \chi}$ is $(\epsilon, s_{sec})\mbox{-}$secure, where $\epsilon = \ngl(n)$ for $s_{sec}=\poly(n)$.
\end{theorem}
\textbf{Note:}  The above theorem is a generalized version of~\cite[Theorem 4.6]{micciancio2013hardness}.  In particular, we note the requirement of sampling from the uniform distribution over some set $\chi \subset \{-\rho,..., \rho\}^m$ is not necessary.  The only requirement in the proof is that $|\chi|\geq m\log \rho$.  Requiring that $\Hoo(\chi) = m\log \rho$ implies that the support of $\chi$ contains at least $2^{m\log \rho}$ elements.  This theorem allows all distributions over a space of size $(2\rho)^m$ that have entropy at least $m\log \rho$.  This means we support all distributions whose entropy gap is no more than $m$ bits.

@@

%\section{Computational Fuzzy Extractors}
%In this section, we show that any computational secure sketch implies a computationally fuzzy extractor using the same paradigm as \lemref{lem:fuzzy ext construction}.  We begin with a formal definition of a computational fuzzy extractor:
%\label{sec:comp fuzzy extractors}
%
%
%Average-case extractors produce pseudorandom bits if the input distribution has high HILL entropy:
%\begin{lemma}
%Let $\ext: \chi \times \zo^d \rightarrow \zo^\ell \times \zo^d$ be a $(k, \epsilon_{ext})$-extractor computable by a circuit of size $s_{ext}$.  Let $X$ be a distribution over $\chi$ with $H^{\hill}_{\epsilon, s_{sec}}(X| Z)\geq k$.  Let, $s' = s_{sec}-s_{ext}$, then 
%$H^{\hill}_{\epsilon+\epsilon_{ext}, s_{sec}}(\ext (X, U_d) | Z, U_d)\geq \ell$.
%\end{lemma}
%%  the same paradigm from 
%%Recall, we defined computational secure sketches using unpredictability entropy~(\defref{def:comp secure sketch}).  It is not known if unpredictability entropy can be extracted from, so we cannot use the construction of \lemref{lem:fuzzy ext construction}.  However, unpredictability entropy implies Yao entropy~(\defref{def:yao entropy}) and this can be extracted from using a reconstructive extractor~(defined in~\cite{barak-computational}).  
%%\begin{definition}
%%An $(\ell, \epsilon)$-reconstruction for a function $\rext:\{0,1\}^n\times \{0,1\}^d\rightarrow \{0,1\}^m\times\{0,1\}^d$~(where the last $d$ outputs are equal to the last $d$ input bits) is a pair of machines $C$ and $D$, where $C:\{0,1\}^n\rightarrow \{0,1\}^\ell$ is a randomized Turing machine and $D^{(\cdot)}:\{0,1\}^\ell\rightarrow \{0,1\}^n$ is a randomized oracle Turing machine which runs in time polynomial in $n$.  Furthermore, for every $x$ and $T$, if $|\Pr[T(\rext(x, U_d)) =1] -\Pr[T(U_m\times U_d)=1]|>\epsilon$, then $\Pr[D^T(C^T(x))=x]>1/2$~(the probability is over the random choices of $C$ and $D$).
%%\end{definition}
%%\begin{lemma}~\cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}
%%\label{lem:unp extraction} 
%%Let $X$ be a distribution with $H^{\unp}_{\epsilon, s_{sec}}(X|Z)\geq k$, and let $\rext$ be an extractor with a $(k-\log 1/\epsilon, \epsilon)$-reconstruction $(C,D)$.  Then $\delta^{\mathcal{D}_{s'}}((\rext(X, U_d), Z), U_m\times U_d\times Z)\leq 5\epsilon,$ where $s'=s_{sec}/(|C|+|D|)$.
%%\end{lemma}
%We are now ready to provide a computational analogue of \lemref{lem:fuzzy ext construction}:
%\begin{lemma}
%Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-computational fuzzy extractor that is $(\epsilon, s_{sec})$ hard with error $\delta$ and denote the range $\rec$ by $\chi$.  Let $\ext:\chi \times \{0,1\}^d\rightarrow \{0,1\}^\ell \times \{0, 1\}^d$ be an $(\tilde{m}, \epsilon_{ext})$ extractor.  Then the following $(\gen , \rep)$ is an $(\mathcal{M}, m, \ell, t)$-computational fuzzy extractor that is $(\epsilon + \epsilon_{ext}, s_{sec}- s_{ext})$-hard with error $\delta$.
%\end{lemma}
%%reconstructive extractor with $(\tilde{m}-\log 1/\epsilon, \epsilon)$-reconstruction $(C, D)$.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, s_{sec}/(|C|+|D|), s_{rec}, 5\epsilon)$-computational fuzzy extractor:
%%\begin{itemize}
%%\item $\gen(w;r, x)$: set $P= (\sketch(w; r), x), R = \rext(w, x)$, and output $(R,P)$.
%%\item $\rep(w', (s, x)):$ recover $w = \rec(w', s)$ and output $R = \rext(w;x)$.
%%\end{itemize}
%%\end{lemma}
%%\begin{proof}
%%Consequence of \defref{def:comp secure sketch} and \lemref{lem:unp extraction}.
%%\end{proof}
%%
%%For completeness, we describe a computational fuzzy extractor based on Construction~\ref{cons:LWESecureSketch} in \secref{sec:fuzzy extractor phrasing}.

@@

\section{Parameter Settings for \consref{cons:informal construction}}
\label{sec:parameter settings}
In this section, we explain the different parameters that go into our construction.  In \thref{thm:lossless secure extractor log} we give a lossless fuzzy extractor from a security parameter $n$ and an error $t$.  In this section, we discuss constraints imposed by 1) efficient decoding 2) maintaining security of the LWE instance and 3) ensuring no entropy loss of the construction.  We begin by reviewing the parameters that make up our construction:

@@

Assuming $n-k = n(1-1/g) > n_0$ and letting $t= c\log n$ we get the following setting:
\begin{align*}
m &= \frac{(c+2d)n}{d}\\
q & = n^f = n^{\frac{m}{n}\frac{\log 2n^{1/2+3\gamma}m}{\log n}} = \poly(n)\\
\rho q &= 2n^{1/2+3\gamma}m = \frac{2(c+2d)n^{3/2+3\gamma}}{d}
\end{align*}
Furthermore, we get decoding in time $O(n^{4d}(n^3\log n))$.  We can output a $k$ fraction of $X$ and the bits will be pseudorandom~(conditioned on $\vA, \vA X+W$).  The parameter $g$ allows is a tradeoff between the number of dimensions needed for security and the size of the field $q$.  In \thref{thm:lossless secure extractor log}, we set $g=2$ and output the first half of $X$.  This analysis proceeds similarly when we desire a linear stretch instead of $m\log \rho q = k\log q$.  %Essentially, this corresponds to multiplying $g$ by the inverse of the desired stretch factor.
